Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-06-06 paper/paper.tex
noise assumption

  assumption that the \gaia\ noise model is correct. If the
  uncertainties are over-estimated then we could be over-deconvolving.

@@

>>>>

  assumption that the \gaia\ noise model is correct, and an additional
  assumption that the parallax uncertainty is always significantly larger
  than the photometric uncertainty in the $J$ band, even after dust correction.
  In the unlikely event (given these choices) that the
  uncertainties are over-estimated, we could be over-deconvolving.

@@

  Since we are explicitly ignoring the (non-Gaussian, in parallax space) photometric
  and dust-extinction uncertainties, our noise estimates are certainly biased, and
  this will translate into small biases in posterior parallax estimates.
